---
title: "Alcohol vs Seat choice"
author: "Jasmin Quintanilla"
date: "summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Our goal is to answer this question is there a difference between the alcohol consumed between the row you choose to sit in??

The data came from UCDavis in the year...

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

# Method
In the data set davisdata is a categorical variable, and alcohol is numerical.

We try to predict alcohol ~ seat so we used the numerical~cat helper file

##Result


##Descriptive results 

##Graphical Summary

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```



This graph shows...

##Numerical Summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical summary shows that

##Inferential Results 

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


The p-value is 0.000006, less than 0.05 so we can reject the null hypothesis.
There is a difference in alchol consumption on where people sit 

```{r}
plot(TukeyHSD(model1))
```


## Conclusions


