---
title: "Alcohol vs Seat choice"
author: "Jasmin Quintanilla"
date: "summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
data(ucdavis1)
davisdata <- read.csv(file="UCDavis.csv")
```


# Introduction
Our goal is to answer this question is there a difference between the alcohol consumed between the row you choose to sit in??

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??  

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

# Method
In the data set davisdata is a categorical variable, and alcohol is numerical.

We try to predict alcohol ~ seat so we used the numerical~cat helper file

##Result


##Descriptive results 

##Graphical Summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```


The graph indicates that alcohol consumption is higher in the back seats compared to both the front and middle seats.

##Numerical Summary

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The numerical summary reveals that the back seats account for approximately 55% of alcohol consumption, the middle seats for 35%, and the front seats for 20%.

##Inferential Results 

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


With a p-value of 0.000006, which is significantly less than the 0.05 threshold, we can reject the null hypothesis. This indicates that there is a statistically significant difference in alcohol consumption based on seating location.

### Get Fancy 

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This graph demonstrates that a higher number of students in the back row consume alcohol compared to those in the front and middle rows.

### Turkeymodel

```{r}
plot(TukeyHSD(model1))
```

The Tukey model indicates a significant difference in alcohol consumption based on seating location. Specifically, the back seats show higher levels of alcohol consumption compared to the front and middle seats.

## Conclusions

Our Goal is to answer this question Is there a difference between the alcohol consumed between the row.$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.$H_A$: The average number drinks is different between at least two rows. The graph shows that the back seats consume more alcohol than both the front or the middle seats.The numerical summary shows that the back seat consumes about 55% where as the middle seat consumes 35%, and the front seats consumes 20%. The p-value is 0.000006, less than 0.05 so we can reject the null hypothesis.
There is a difference in alcohol consumption on where people sit. This graph shows that there are more students sitting in the back who drink alcohol than the front and middle row. The turkey model shows there is a difference when seating in the back rather then the front or middle. The back consumes more levels of alcohol than the front or middle. 


